resistanceModelNotesAndy

### 2015-07-06 resistanceModelNotesAndy.Rmd
notes

@@

@@

@@

1. work on sensiPostProc() It will need to be quite clever. It will take the output files from insecticide1, insecticide2 and mixture and use these to calculate timeToResistance critical points for sequential, mixture1 & mixture2 scenarios. Try to make it as modular as possible.

@@

@@

1. maybe separate out classification trees from sensiAn1

@@

1. write a function to calculate timeToThreshold for all scenarios based on listOut, allow user to specify which locus.

@@

### outputs ###
From runModel2()
A list of 3 lists of one or more scenarios: 
1. results : by generation freq of R allele at each loci in each sex plus linkage stuff
    columns include Gen, m.R1, m.R2, f.R1, f.R2
2. genotype : frequencies of each of the ten genotypes, per generation
3. fitness : fitness scores of each genotype/niche combination (table 4. of Main Document)
4. input
e.g. 
listOut$results[1] gives a results matrix for the first scenario
listOutMix$input gives the inputs for all scenarios

>>>>

** 31/6/15 **
Quick review of what needs to go into the final decision tree.

slight rethink : I want the input files to be mostly the same for I1,I2 & mixture, so that they can be added together in combined scenarios.

I added a set.seed into sensiAnPaperPart()
This shows the input files for diffeerent insecticide strategies are now the same.

tst <- listOutMix$input[c('P_1','P_2','a.f_AB','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B'),]
#note a.f_A0 rather than a.f_AB
tst2 <- listOutI1$input[c('P_1','P_2','a.f_A0','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B'),]
identical(as.numeric(tst),as.numeric(tst2))

@@

1. CHECK MODEL RUNS ARE DOING WHAT I THINK. Currently seems that resistance is quicker for mixtures under all scenarios (or very nearly all)

@@

1. review how to answer these questions.
Main question is : Tree1 is mixture better (0/1), Tree2 is mixture better by >20%.

@@

1. work further on sensiAnPaper1All

1. decide whether to do main runs with P_2 dependent on P_1 or not

@@

Main question is : Tree1 is mixture better (0/1), Tree2 is mixture better by >20%.

@@

@@

@@

### outputs ###
From runModel2()
A list of 3 lists of one or more scenarios: 
1. results : by generation freq of R allele at each loci in each sex plus linkage stuff
    columns include Gen, m.R1, m.R2, f.R1, f.R2
2. genotype : frequencies of each of the ten genotypes, per generation
3. fitness : fitness scores of each genotype/niche combination (table 4. of Main Document)
4. input
e.g. 
listOut$results[1] gives a results matrix for the first scenario
listOutMix$input gives the inputs for all scenarios
listOutMix$input[c('P_1','P_2'),] gives selected inputs
